Testing Education State Transitions

### 2023-06-15 minos/testing/education_transitions.Rmd
Added some more plots for testing what age people achieve different education levels, as well as a plot showing mean age when level achieved

@@

>>>>

ggplot(data = filter(raw, education_state == 0), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 0')

ggplot(data = filter(raw, education_state == 1), aes(x = age)) +
  geom_histogram() +
  labs(title = 'Education State == 1')

@@

Mean ages.

raw.meanAge <- raw %>%
  group_by(education_state) %>%
  summarise(age = mean(age))

ggplot(data = raw.meanAge, aes(x = education_state, y = age)) +
  geom_col()
